Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-30 evaluation.tex
Added 10% overhead data.

\subsection{Coverage with Adjustable Overheads}

@@

We see that by varying the overhead budget, the coverage achieved also varies.
With only a 50\% overhead budget, array bounds check still
achieves 83\% monitoring coverage on average. This overhead budget corresponds
to just 20\% of the average overheads seen by BC after filtering only. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing monitoring coverage without
introducing overheads. The second effect is that, although we aggressively
filter out monitoring events, there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring. We see that
with a 50\% overhead budget, UMC achieves 51\% monitoring coverage on average.
Again, this overhead budget corresponds to only 20\% of the overheads seen by UMC
with filtering only.

>>>>

\subsection{Coverage with Adjustable Partial Monitoring}

@@

We see that by varying the overhead budget, the coverage achieved also varies.
With only a 10\% overhead budget, array bounds check still
achieves 82\% monitoring coverage on average. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing monitoring coverage without
introducing overheads. The second effect is that, although we aggressively
filter out monitoring events, there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring. We see that
with a 10\% overhead budget, UMC achieves 32\% monitoring coverage on average
and with a 50\% budget, UMC achieves 51\% coverage.

### 2014-05-30 introduction.tex
Added 10% overhead data.

% Evaluation
In order to evaluate our approach, we applied it to 3 different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
Our experiments show that filtering reduces the average overhead of these
monitors from 7-18x down to 13-300\%.
In addition, with partial monitoring, for the monitoring schemes which still
see average overheads of 300\%, we show that with just 50\% overheads, we can still
provide 51-83\% of coverage on average. By increasing the
overhead budget, this coverage rate can be increased.

>>>>

% Evaluation
In order to evaluate our approach, we applied it to 3 different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
Our experiments show that filtering reduces the average overhead of these
monitors from 7-18x down to 13-300\%.
In addition, with partial monitoring, for the monitoring schemes which still
see average overheads of 300\%, we show that with just 10\% overheads, we can still
provide 32-82\% of coverage on average. By increasing the
overhead budget, this coverage rate can be increased.

### 2014-05-30 title.tex
Added 10% overhead data.

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that can be
used to filter out unnecessary monitoring and enable adjustable partial monitoring.
The dataflow engine can identify events with null metadata so that they can
be filtered out. To further reduce the overhead of monitoring, we propose
to enable a trade-off between monitoring coverage and overhead by dropping certain
monitoring operations. For this partial monitoring, the dataflow engine is used
to track dropped monitoring flows so that false positives can be avoided.
Given the architecture, we also investigate how the dropping decisions should be
made for partial monitoring and show that there exists a trade-off between closely
matching an overhead target and the coverage that can be achieved.
% Our experiments show that the system is able to
% closely meet the target overhead and achieve significant monitoring coverage
% for reasonable overhead targets.
The experimental results show that filtering can significantly reduce monitoring
overheads from 7x-18x on average, depending on the monitoring scheme, to
13\%-300\%. Additionally, for the monitoring schemes which still show 300\%
average overhead, partial monitoring can reduce this overhead to 50\% while
still achieving 51-83\% average monitoring coverage.

>>>>

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that can be
used to filter out unnecessary monitoring and enable adjustable partial monitoring.
The dataflow engine can identify events with null metadata so that they can
be filtered out. To further reduce the overhead of monitoring, we propose
to enable a trade-off between monitoring coverage and overhead by dropping certain
monitoring operations. For this partial monitoring, the dataflow engine is used
to track dropped monitoring flows so that false positives can be avoided.
Given the architecture, we also investigate how the dropping decisions should be
made for partial monitoring and show that there exists a trade-off between closely
matching an overhead target and the coverage that can be achieved.
% Our experiments show that the system is able to
% closely meet the target overhead and achieve significant monitoring coverage
% for reasonable overhead targets.
The experimental results show that filtering can significantly reduce monitoring
overheads from 7x-18x on average, depending on the monitoring scheme, to
13\%-300\%. Additionally, for the monitoring schemes which still show 300\%
average overhead, partial monitoring can reduce this overhead to 10\% while
still achieving 32-82\% average monitoring coverage.
